PanLex-RDF

### 2013-01-01 paper/2012/SWJ-PanLex/paper.tex
added approver count
My changes

%\author[1]{\fnms{Patrick} \snm{Westphal}},
%\author[1]{\fnms{Claus} \snm{Stadler}},
%\author[2]{\fnms{Jonathan} \snm{Pool}}
%\address[1]{University of Leipzig, Institute of Computer Science, AKSW}
%\address[2]{TODO}

@@

\begin{abstract}
At present, there are approximately 7,000 living languages in the world.
However, some experts claim that the process of globalization may eventually lead
to the world losing this linguistic diversity.
The vision of the PanLex project is to save these languages, especially low-density ones,
by allowing them to be intertranslatable and thus to be a part of the Information Age.
For this reason, PanLex gathers and integrates information from thousands of
linguistic resources, such as monolingual dictionaries, bilingual dictionaries, multilingual dictionaries,
glossaries, standards and thesauri.
In this paper we describe how we transformed this data to RDF, interlinked it with
lexvo and DBpedia and published it as Linked Data and SPARQL.
\end{abstract}

@@

\begin{figure}
\centering
\includegraphics[width=0.4\textwidth]{images/PanLex-SW-Architecture}
\caption{PanLex architecture}
\label{fig:panlex-architecture}
\end{figure}

\todo{Fix the image: It should also show some sources which panlex uses.}

@@

\section{Conclusions and Future Work}
\label{sec:conclusion}
In this paper we describe the PanLex database and its conversion to RDF.
Based on our URI and vocabulary design, we created appropriate view definitions
for the virtual RDB to RDF solution \emph{Sparqlify} which carries out
the actual RDF transformation.
Furthermore, we interlinked the languages in PanLex with lexvo,
and created about 2.5 million links to DBpedia for expressions in 16 languages.
%We detailed the developed vocabulary and

>>>>

%patrick.westphal@studserv.uni-leipzig.de
%\author[1]{\fnms{Patrick} \snm{Westphal}},
%\author[1]{\fnms{Claus} \snm{Stadler}},
%\author[2]{\fnms{Jonathan} \snm{Pool}}
%\address[1]{University of Leipzig, Institute of Computer Science, AKSW}
%\address[2]{TODO}

@@

\begin{abstract}
At present, there are approximately 7,000 living languages in the world.
However, some experts claim that the process of globalization may eventually lead
to the world losing this linguistic diversity.
The vision of the PanLex project is to save these languages, especially low-density ones,
by allowing them to be intertranslatable and thus to be a part of the Information Age.
For this reason, PanLex gathers and integrates information from thousands of
linguistic resources, such as monolingual dictionaries, bilingual dictionaries, multilingual dictionaries,
glossaries, standards and thesauri.
In this paper we describe how we transformed this data to RDF, interlinked it with
Lexvo and DBpedia and published it as Linked Data and SPARQL.
\end{abstract}

@@

\begin{figure}
\centering
\includegraphics[width=0.4\textwidth]{images/PanLex-SW-Architecture-New}
\caption{PanLex architecture}
\label{fig:panlex-architecture}
\end{figure}

@@

\section{Conclusions and Future Work}
\label{sec:conclusion}
In this paper we describe the PanLex database and its conversion to RDF.
Based on our URI and vocabulary design, we created appropriate view definitions
for the virtual RDB to RDF solution \emph{Sparqlify} which carries out
the actual RDF transformation.
Furthermore, we interlinked the languages in PanLex with Lexvo,
and created about 2.5 million links to DBpedia for expressions in 16 languages.
%We detailed the developed vocabulary and
